Continuous Generalization of Buildings \\ by Growing and Aggregating

### 2017-09-15 ContinuousGeneralisation_Paper/ContinuousGeneralisation_Paper_Sigspatial/PaperBody.tex
improved our method

At time $t=1$, we know that 
which buildings will finally be aggregated into the same built-up area
(see \sect\ref{sec:Group}).
We connect each pair of these buildings by adding a line segment linking the 
nearest points.
If we consider each building as a node and each line segment as an edge, 
then we have a graph.
Using Prim's algorithm \citep{Prim1957}, 
we find a minimum spanning tree (MST) in the graph,
taking the lengths of the line segments as the weights.
As a results, the line segments corresponding to the edges in the MST
are used as bridges.
At any time $t$, we pick some of the bridges to aggregate the buildings.
Then we grow the bridged buildings (see \fig\ref{fig:GrowAndBridge}).
No matter a bridge appears earlier or later, 
it has width $2\dtrm{G}$ at time $t$.
This setting guarantees that no bridge is thin when $t=1$.
We do not introduce bridges according to nearest points at time $t$
because the nearest points may change (see \fig\ref{fig:NearestPoints} for 
example).

@@

We would like to use $\dtrm{E}=\frac{l}{2} \cdot M_t$ so that
any pits and spikes narrower than $l$ will be removed. 
We set $l=0.3\,\mathrm{mm}$, 
which was used as a length threshold by, for example, 
\citet{Regnauld2001}.
Distance $\dtrm{G}$ can be arbitrarily small according to \eq\ref{eq:d_Gt}, 
but $\dtrm{E}$ is at least $\frac{l}{2} M_\mathrm{s}$. 
In this case, $\dtrm{G}-\dtrm{E} \le 0$ when $t$ is small, 
which violates \eq\ref{eq:d_Dt}, where $\dtrm{D}>0$.
As a compromise, we use
\begin{equation}
\label{eq:d_Et}
\dtrm{E} =t \cdot \frac{l}{2} M_\mathrm{g}.
\end{equation}
%Still, we should make sure that $\dtrm{G}-\dtrm{E} > 0$, which means
%$t \cdot \frac{\lambda}{2}\sqrt{a} (M_\mathrm{g}-M_\mathrm{s})-
%t \cdot \frac{l}{2} M_\mathrm{g} >0$.
Still, we should make sure that $\dtrm{G}-\dtrm{E} > 0$, which means
$t \cdot d_\mathrm{G} - t \cdot \frac{l}{2} M_\mathrm{g} >0$.
As a result, we should make sure that
\begin{equation}
\label{eq:S_g}
M_\mathrm{g} < \frac{2 d_\mathrm{G}}{l}.
\end{equation}

@@

\begin{figure*}[tb]
	\centering
	\includegraphics[draft=false]{RemoveBay}
	\caption{Group buildings iteratively.
		(a) Original buildings.
		(b) Dilate each original building with distance 
		$\dtrm{G}+\dtrm{D}$.		
		(c) Erode the dilated polygons with distance $\dtrm{D}$.
		(d) Dilate the eroded polygons with distance $\dtrm{C}$. 
		If two polygons in (d) intersect, 
		the original buildings will be put in the same group 
		because they will become too close at time $t$.
		There two groups according to (d).
		One consists of the single middle building and 
		the surrounding $9$ buildings comprise the other group.
		(e) The result of growing and merging at time $t$ 
		if we use $\dtrm{D}=0$.
		The process of (f), (g), and (h) is similar to 
		that of (b), (c), and (d).		
		The difference is that 
		instead of applying the operators to each single building, 
		we do that for the buildings in the same group.
		In (f), we manage to remove the bay in (e) by additionally dilating 
		with distance $\dtrm{D}$.
		There is only one group left according to (h).
		We iteratively group buildings in this way until the number of groups 
		does not decrease.
	}
	%in this example, we used _dblTotalGrow *= 5;
	\label{fig:RemoveBay}
\end{figure*}

>>>>

At time $t=1$, we know that 
which buildings will finally be aggregated into the same built-up area
(see \sect\ref{sec:Group}).
We connect each pair of these buildings by adding a line segment linking the 
nearest points.
If we consider each building as a node and each line segment as an edge, 
then we have a graph.
Using Prim's algorithm \citep{Prim1957}, 
we find a minimum spanning tree (MST) in the graph,
taking the lengths of the line segments as the weights.
As a results, the line segments corresponding to the edges in the MST
are used as bridges.
A bridge is then picked to aggregate two buildings at time $t$ 
if they become too close.
We grow the bridged buildings (see \fig\ref{fig:GrowAndBridge}).
No matter a bridge appears earlier or later, 
it has width $2\dtrm{G}$ at time $t$.
This setting guarantees that no bridge is thin when $t=1$.
We do not introduce bridges according to nearest points at time $t$
because the nearest points may change (see \fig\ref{fig:NearestPoints} for 
example).

@@

We would like to use $\dtrm{E}=\frac{l}{2} \cdot M_t$ so that
any pits and spikes narrower than $l$ will be removed. 
We set $l=0.3\,\mathrm{mm}$, 
which was used as a length threshold by, for example, 
\citet{Regnauld2001}.
Distance $\dtrm{G}$ can be arbitrarily small according to \eq\ref{eq:d_Gt}, 
but $\dtrm{E}$ is at least $\frac{l}{2} M_\mathrm{s}$. 
In this case, $\dtrm{G}-\dtrm{E} \le 0$ when $t$ is small, 
which violates \eq\ref{eq:d_Dt}, where $\dtrm{D}>0$.
As a compromise, we set erosion distance
\begin{equation}
\label{eq:d_Et}
\dtrm{E} =t \cdot \frac{l}{2} M_\mathrm{g}.
\end{equation}
%Still, we should make sure that $\dtrm{G}-\dtrm{E} > 0$, which means
%$t \cdot \frac{\lambda}{2}\sqrt{a} (M_\mathrm{g}-M_\mathrm{s})-
%t \cdot \frac{l}{2} M_\mathrm{g} >0$.
Still, we should make sure that $\dtrm{G}-\dtrm{E} > 0$, which means
$t \cdot d_\mathrm{G} - t \cdot \frac{l}{2} M_\mathrm{g} >0$.
As a result, we should make sure that
\begin{equation}
\label{eq:S_g}
M_\mathrm{g} < \frac{2 d_\mathrm{G}}{l}.
\end{equation}

@@

\begin{figure*}[tb]
	\centering
	\includegraphics[draft=false]{RemoveBay}
	\caption{Group buildings iteratively.
		(a) Original buildings.
		(b) Dilate each original building with distance 
		$\dtrm{G}+\dtrm{D}$.		
		(c) Erode the dilated polygons with distance $\dtrm{D}$.
		(d) Dilate the eroded polygons with distance $\dtrm{C}$. 
		If two polygons in (d) intersect, 
		the original buildings will be put in the same group 
		because they will become too close at time $t$.
		There are two groups according to (d).
		One consists of the single middle building and 
		the surrounding $9$ buildings comprise the other group.
		(e) The result of growing and merging at time $t$ 
		if we use $\dtrm{D}=0$.
		The process of (f), (g), and (h) is similar to 
		that of (b), (c), and (d).		
		The difference is that 
		instead of applying the operators to each single building, 
		we do that for the buildings in the same group.
		In (f), we manage to remove the bay in (e) by additionally dilating 
		with distance $\dtrm{D}$.
		There is only one group left according to (h).
		We iteratively group buildings in this way until the number of groups 
		does not decrease.
	}
	%in this example, we used _dblTotalGrow *= 5;
	\label{fig:RemoveBay}
\end{figure*}
